Manuscript

### 2015-02-17 inst/simulation/manuscript.Rmd
...

```{r table-2}
intersections <- getIntersections(scenarios)
intersections2000 <- getIntersections(scenarios=paste0(scenarios, "combined"))
intersections10days <- getIntersections(scenarios=paste0(scenarios, "10days"))
intersectionsx <- plyr::join(populationSizes, intersections)
intersections2000x <- plyr::join(populationSizes2000, intersections2000)
intersections10daysx <- plyr::join(populationSizes10Days, intersections10days)
i.stat <- function(x) data.frame(o.mean=mean(x$Observed), o.sd=sd(x$Observed), e.mean=mean(x$Estimated), e.sd=sd(x$Estimated),
                                 pp.mean=round(mean(x$Estimated/x$Observed), 2), pp.sd=round(sd(x$Estimated/x$Observed), 2),
                                 i.mean=mean(x$intersections), i.sd=sd(x$intersections), ip.mean=round(mean(x$intersections/x$Observed),2), ip.sd=round(sd(x$intersections/x$Observed),2))
ddply(intersectionsx, .(Scenario, modelName), i.stat)
ddply(intersections2000x, .(Scenario, modelName), i.stat)
ddply(intersections10daysx, .(Scenario, modelName), i.stat)

rer.stat <- function(x) data.frame(RERMean=round(mean(x$intersections/x$Observed),2), RERSD=round(sd(x$intersections/x$Observed),2))
ddply(intersectionsx, .(Scenario), rer.stat)
ddply(intersections2000x, .(Scenario), rer.stat)
ddply(intersections10daysx, .(Scenario), rer.stat)
#writeTable(subset(logTable1, Model != "VT"), "table-1a.docx", context)

@@

plotPopulationCorrelations <- function(populationCorrelations) {
  p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
  return(p)
}
```

@@

```{r figure-5-init}
getCIProportions <- function(scenarios, modelNames, panel, scenarioNames) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeOverEstimate=Inf)
  a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames)
  b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames, probs=c(.25, .75), probsName="50%")
  credibilityIntervals <- rbind(a, b)
  credibilityIntervals$panel <- panel
  credibilityIntervals$scenario <- rep(scenarioNames, times=2, each=length(modelNames))
  return(credibilityIntervals)  
}

plotCIProportions <- function(credibilityIntervals) {
  modelLabels <- prettyModelName(unique(credibilityIntervals$modelName))
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=CI, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("darkgray", "black"), labels=modelLabels) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion within CI") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank())
  return(p)
}
```

```{r figure-5abc}
cip1 <- getCIProportions(scenarios=scenarios, modelNames=modelNames[1:3], panel="a", scenarioNames=scenarios)
cip2 <- getCIProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[1:3], panel="b", scenarioNames=scenarios)
cip3 <- getCIProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[1:3], panel="c", scenarioNames=scenarios)
cip <- subset(rbind(cip1, cip2, cip3), modelName != "SmoothModel-nbinomial-ar1")
p <- plotCIProportions(cip)
saveFigure(p, "manuscript-figure-5.png", width=6, height=2)

>>>>

```{r table-2}
intersections <- getIntersections(scenarios)
intersections2000 <- getIntersections(scenarios=paste0(scenarios, "combined"))
intersections10days <- getIntersections(scenarios=paste0(scenarios, "10days"))
intersectionsx <- plyr::join(populationSizes, intersections)
intersections2000x <- plyr::join(populationSizes2000, intersections2000)
intersections10daysx <- plyr::join(populationSizes10Days, intersections10days)
#i.stat <- function(x) data.frame(o.mean=mean(x$Observed), o.sd=sd(x$Observed), e.mean=mean(x$Estimated), e.sd=sd(x$Estimated),
#                                 pp.mean=round(mean(x$Estimated/x$Observed), 2), pp.sd=round(sd(x$Estimated/x$Observed), 2),
#                                 i.mean=mean(x$intersections), i.sd=sd(x$intersections), ip.mean=round(mean(x$intersections/x$Observed),2), ip.sd=round(sd(x$intersections/x$Observed),2))
#ddply(intersectionsx, .(Scenario, modelName), i.stat)
#ddply(intersections2000x, .(Scenario, modelName), i.stat)
#ddply(intersections10daysx, .(Scenario, modelName), i.stat)

rer.stat <- function(x) data.frame(RERMean=round(mean(x$intersections/x$Observed),2), RERSD=round(sd(x$intersections/x$Observed),2))
i <- ddply(intersectionsx, .(Scenario), rer.stat); i$Scenario=prettyScenario(i$Scenario)
i2000 <- ddply(intersections2000x, .(Scenario), rer.stat); i2000$Scenario=prettyScenario(i2000$Scenario)
i10days <- ddply(intersections10daysx, .(Scenario), rer.stat); i10days$Scenario=prettyScenario(i10days$Scenario)

writeTable(i, "table-2a.docx", context)
writeTable(i2000, "table-2b.docx", context)
writeTable(i10days, "table-2c.docx", context)
```

@@

plotPopulationCorrelations <- function(populationCorrelations) {
  populationCorrelations$Scenario <- prettyScenario(populationCorrelations$Scenario)
  p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  scale_y_continuous(limits=c(-1,1)) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
  return(p)
}
```

@@

```{r figure-5-init}
getCIProportions <- function(scenarios, modelNames, panel, scenarioNames, cutoff=Inf) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeOverEstimate=cutoff)
  a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames)
  b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames, probs=c(.25, .75), probsName="50%")
  credibilityIntervals <- rbind(a, b)
  credibilityIntervals$panel <- panel
  credibilityIntervals$scenario <- rep(scenarioNames, times=2, each=length(modelNames))
  return(credibilityIntervals)  
}

plotCIProportions <- function(credibilityIntervals) {
  modelLabels <- prettyModelName(unique(credibilityIntervals$modelName))
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=CI, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("black", "darkgray"), labels=modelLabels) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion within CI") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank())
  return(p)
}
```

```{r figure-5abc}
cip1 <- getCIProportions(scenarios=scenarios, modelNames=modelNames[1:3], panel="a", scenarioNames=scenarios, cutoff=cutoff)
cip2 <- getCIProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[1:3], panel="b", scenarioNames=scenarios, cutoff=10*cutoff)
cip3 <- getCIProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[1:3], panel="c", scenarioNames=scenarios, cutoff=cutoff)

#cip1 <- getCIProportions(scenarios=scenarios, modelNames=modelNames[1:3], panel="a", scenarioNames=scenarios)
#cip2 <- getCIProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[1:3], panel="b", scenarioNames=scenarios)
#cip3 <- getCIProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[1:3], panel="c", scenarioNames=scenarios)

cip <- subset(rbind(cip1, cip2, cip3), modelName != "SmoothModel-nbinomial-ar1")
p <- plotCIProportions(cip)
saveFigure(p, "manuscript-figure-5.png", width=6, height=2)
